---
title: 'Data Science Project Guide: Honey and Bees'
author: "TechAcademy e.V."
date: "Summer Term 2022"
geometry: top=0.5in, bottom=1.5in, left=1in, right=1in, a4paper
fontsize: 11pt
fontfamily: mathpazo
bibliography:
- book.bib
- packages.bib
biblio-style: apalike
link-citations: yes
urlcolor: blue
description: Everything you need to know for your successful TechAcademy Data Science
  Project
site: bookdown::bookdown_site
editor_options: 
  markdown: 
    wrap: sentence
---

```{r eval=FALSE, include=FALSE}
install.packages("bookdown")
install.packages("tinytex")
library(tinytex)
# or the development version
# devtools::install_github("rstudio/bookdown")
```

```{r global_options, include=FALSE}
# knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
#                       echo=FALSE, warning=FALSE, message=FALSE)
knitr::opts_chunk$set(fig.width=12, fig.height=8,
                      warning=FALSE, message=FALSE, comment=">")
#echo=FALSE,
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

\clearpage

```{=tex}
\addtolength{\headheight}{17.82275pt}
\rhead{\includegraphics[height=0.5cm]{plot/TA_logo.png}}
```
```{=tex}
\fancyfoot{}
\fancyfoot[R]{\thepage}
\addtolength{\headheight}{17.82275pt}
```
\fancyfoot[L]{Data Science Project Guide | Honey and Bees | \copyright\ 2022, TechAcademy e.V.}

```{=tex}
\renewcommand{\headrulewidth}{0.25pt}
\renewcommand{\footrulewidth}{0.25pt}
```
```{=tex}
\tableofcontents
\clearpage
```


# Welcome!

If you are a beginner, the first few chapters will introduce the basics of the R and Python tracks respectively and you will find helpful explanations to questions you might have in the beginning of your coding journey. If you are already advaced, it might be still worth a read. 
There will be a quick introduction to the Data Science track for you to get started with the project quickly. Let’s start with the basics!
In all tracks you will work on your project in small groups with your peers. Not only will this help you to get the project done faster, but we also want you to compare your results and discuss your findings – remember, coding is just half the effort, understanding what the data and the output shows is even more important! Our experience shows: The different backgrounds of the members and discussing different opinions and ideas will produce the best results. Besides, it is way more fun to work on a project together than to code alone!

Your group should consist of approximately four team members. You can choose your teammates independently; we will not interfere with your arrangements. However, we can assist you to find your team members. It is important that all group members complete the same level of difficulty (beginner or advanced), since the tasks are different in scope for each level. We explicitly encourage you to collaborate with students from different university faculties. This not only allows you to get to know people from other faculties, but may also give you a whole new perspective on the project and tasks. When submitting your project please note: for a certificate, each person must submit the project individually. However, hand-ins may be similar within your group. You can get more information at our first Coding Meetup on **May 18, 2022.**

Every semester, the Product Development Team at TechAcademy thinks hard about a new project that is suited for you to learn data science.
This semester we decided to analyse a simple yet important part of our lives: honey and bees. While honey might not be the reason why we still exist on this planet, bees very well are, hence why honey production may also be. However, with climate change and increasing globalization, bee colonies are threatened daily. Though none of us are experts on bees and climate, we still believe that together we can all learn a lot from this case study.

This case study and the associated project guide was developed and written entirely from scratch by TechAcademy’s Data Science team. Inga Lasys and Isabel Schnorr developed the project in `R`, while Thilo Leitzbach developed it in `Python`.

